A Large-Scale Study of the Use of Eval in R

### 2020-08-21 inst/paper/main.tex
stuff

\title{A Study of the Usage of Eval in R}

\author{\IEEEauthorblockN{For double blind review}%
  %\IEEEauthorblockA{ dept} \\ \and
}  
\maketitle

@@

\begin{abstract}

\end{abstract}

@@

The \c{eval} function has a bad reputation. This function, under one name or
another and with various exact semantics, is available in many dynamic
languages. It is used to transform text into code and execute that code.

@@

Why do we do this dynamically? Because it raises a chicken-and-egg problem,
doing it statically would require us to reason about eval based code which may
not be possible in general.

@@

- cannot replace with (cite study of with construct).
- 
\textbf{*}

@@

\section{Eval in R}
- Talk about environments
- How is it different from JS (takes language, env in R but string in JS).

>>>>

\title{A Large-Scale Study of the Use of Eval in R}
\author{\vspace{-.8cm}\IEEEauthorblockN{\it\Large The Eval that Data Scientist Do}%
  %\IEEEauthorblockA{ dept} \\ \and
}  
\maketitle

@@

\begin{abstract}
  The eval function turns text into code and thus causes difficulties for
  reasoning about the behavior of software that uses it. This paper is a
  study of the usage of eval in R, a widely used data science programming
  language. We combine static and dynamic analysis on a large and
  representative corpus of R programs. Our results show...
\end{abstract}

@@

The \c{eval} function has a bad reputation. This function, under one name or
another and with various exact semantics, is available in many dynamic
languages. It is used to transform text into code and execute that code.  It
earned its reputation because of the challenges it poses for reasoning about
code that uses it.  The problem with eval is that the behavior of a system
departs from the source text of the program and becomes dependent on the
program's inputs. This brings challenge to program analysis and security.

While the worst case is indeed pretty bad, previous work has found that
in many cases eval can be fairly inoccuous or at least much less dangerous
that the worst case.

There has been research in understanding the behavior of eval in the context
of web programming and in particular the JavaScript language.

This paper looks at eval in the context of data science. We look at the use
of eval in the R programming language. And in particular we look at its use
in three different contexts.  The first context is the implementation of the
language, how is eval used by the core developers of R in the packages that
are part of the R virtual machine.  The secoond context is how it is used in
libraries. And the third context is how it is used by end users of the
language.

There are reasons to believe that usage patterns may be different. The core
R code is extremely stable, it has only been maintained for the last 20
years with very few far reaching changes. The libraries represent a more
lively ecosystem with new libraries added each day. Typically they are
developped by experience R developer.  Finally, end user code is often
written by non-programmers, data scientists who may or may not understand R.

To set up our experiements we have created a corpus composed of three
distinct data sets.  We have set out the 8 packages that are included with
the R virtual machine and refer to these as `` base'' packages.  We have
selected the 400 most widely included libraries and obtained a number of
client programs to exercises them.  Finally we have obtained 400 end users
programs from the Kaggle competition.

To understand the behavior of eval we perform a combination of static
analysis, dynamic analysis and manual inspection. The results presented
here summarize our findings.

Our infrastructure is publicly available, released in open source, and our
data, and code will be submitted to artifact evaluation.

@@

@@

- cannot replace with (cite study of with construct).

@@

Previous work looked at eval in JavaScript

\section{Shade of Eval}

- Talk about environments
- How is it different from JS (takes language, env in R but string in JS).
